### 2016-07-18 version0.0/asli.tex
Completed intro.
Completed paper1 and 3
All chapter done
Added CV

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref}%comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage[font=small,labelfont=bf]{caption}
\DeclareCaptionFont{tiny}{\tiny}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{adjustbox}

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
\newcommand{\halpha}    {H$\alpha $\ }
\newcommand{\um}    {$\mu$m\ }
\newcommand{\mice} {$\mu$m}
\newcommand{\nprime}{N$^\prime$}
\newcommand{\eqnprime} {N^\prime}
\newcommand{\degr} {$^{\circ}$}
\newcommand{\arcmin} {$^{\prime}$}
\newcommand {\arcsec} {$^{\prime\prime}$}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX\ }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc ii}]} 
\newcommand \oiii {[O~{\textsc iii}]} 
\newcommand \hi {H~{\textsc i}}
\newcommand \hii {H~{\textsc ii}}
\newcommand \oii {[O~{\textsc ii}]}
\newcommand \nii {[N~{\textsc ii}]}

@@

\vfill
\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
\newpage
\tableofcontents\newpage
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
\addcontentsline{toc}{chapter}{List of Appendices}
\listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
\end{preliminary}
%% End of the preliminary sections: reset page style and numbering.

@@

% \include{intro0.01}
 \include{paper1}
%\include{paper3}
%\include{paper2}
% \include{summary}

@@

% %Appendices.
% \begin{appendices}
% \include{appendixa}
% \include{appendixa_2}
% \include{appendixb}
% \include{appendixc}
% \end{appendices}

%CV only relevant stuff... not full CV.
% \addcontentsline{toc}{chapter}{Curriculum Vitae}
% \chapter*{Curriculum Vitae}
% \begin{table}[ht]
% \begin{tabular}{ll}
% \textbf{Name:} & \firstname{} \lastname\\\\
% \textbf{Post-Secondary} & La La School\\
% \textbf{Education and}& La La Land\\
% \textbf{Degrees:}& 1996 - 2000 M.A.\\\\
% & University of Western Ontario\\
% & London, ON\\
% & 2008 - 2012 Ph.D.\\\\
% \textbf{Honours and}& NSERC PGS M\\
% \textbf{Awards:}& 2006-2007\\\\
% \textbf{Related Work}& Teaching Assistant\\
% \textbf{Experience:}& The University of Western Ontario\\
% & 2008 - 2012\\
% \end{tabular}
% \end{table}
% \subsubsection*{Publications:}
% La La
\end{document}

>>>>

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage[draft=false]{hyperref}%comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage[font=small,labelfont=bf]{caption}
\DeclareCaptionFont{tiny}{\tiny}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{adjustbox}

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
\newcommand{\halpha}    {H$\alpha $}
\newcommand{\um}    {$\mu$m\ }
\newcommand{\mice} {$\mu$m}
\newcommand{\nprime}{N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand{\eqnprime} {N^\prime}
\newcommand{\degr} {$^{\circ}$}
\newcommand{\arcmin} {$^{\prime}$}
\newcommand {\arcsec} {$^{\prime\prime}$}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX\ }
\newcommand \GALEX {GALEX\ }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~\textsc{ii}]} 
\newcommand \oiii {[O~\textsc{iii}]} 
\newcommand \hi {H~\textsc{i}}
\newcommand \hii {H~\textsc{ii}}
\newcommand \oii {[O~\textsc{ii}]}
\newcommand \nii {[N~\textsc{ii}]}

@@

\vfill
\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
\newpage
\tableofcontents\newpage
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
% \addcontentsline{toc}{chapter}{List of Appendices}
% \listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
\end{preliminary}
%% End of the preliminary sections: reset page style and numbering.

@@

\include{intro0.01}
\include{paper1}
\include{paper3}
\include{paper2}
\include{summary}

@@

% %Appendices.
 \begin{appendices}
 \include{appendixa}
 \include{appendixa_2}
 \include{appendixb}
\include{appendixc}
 \end{appendices}

%CV only relevant stuff... not full CV.
 \addcontentsline{toc}{chapter}{Curriculum Vitae}
\chapter*{Curriculum Vitae}
\begin{table}[ht]
\begin{tabular}{ll}
\textbf{Name:} & \firstname{} \lastname\\\\
\textbf{Post-Secondary} & {\sl Doctor of Philosophy,} Astronomy \\
\textbf{Education and}& Western University\\
\textbf{Degrees:}& London, ON\\
& 2012 - 2016\\\\
&{\sl Master of Science,} Astronomy \\
& University of Sussex \\
& Brighton, England\\
& 2011 - 2012\\\\
& {\sl Bachelor of Science,} Physics \\
& Sharif University of Technology \\
& Tehran, Iran \\
& 2006 - 2011\\\\
\textbf{Honours and}& {\sl Western University Graduate Research Scholarship}\\
\textbf{Awards:}&(2012-2016)\\\\
& {\sl Travel Grant for Statistical Challenges in Modern Astronomy VI,}\\
&  Pittsburgh, PA (Spring, 2016)\\\\
% &{\sl Travel Grant for Canadian Astronomical Society Conference (CASCA),} \\
% & Winnipeg, MA (Spring, 2016)\\
&{\sl Scholarship for Utrecht Summer School on Star formation,}\\
&Utrecht, Netherlands (Summer, 2009)\\\\
\textbf{Related Work}& Graduate Research \& Teaching Assistant\\
\textbf{Experience:}& Western University\\
& 2012 - 2016\\\\
% & Instructor for Software Carpentry\\
% & 2015 - 2016\\\\
&Graduate Research Assistant\\
& University of Sussex \\
& 2011 - 2012\\\\
\end{tabular}
\end{table}

\subsubsection*{Publications:}
 \textbf{Rahmani. S}, Lianou. S, Barmby. P, ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
\textbf{Rahmani. S}, Teimoorinia. H, Barmby. P, `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, JUNE,2016\\

\subsubsection*{Work in Preparation}
 \textbf{Rahmani. S}, Teimoorinia. H, Peeters. E, Barmby. P, `` {\em Data Mining in nearby galaxies}", In prep.\\

\subsubsection*{Conferences Talks}

{\sl Canadian Astronomical Society Conference (CASCA), Winnipeg, MA}\hfill(2016)
\begin{itemize} 
\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
\end{itemize}

{\sl International Tusi Conference on Astrophysics, devoted to the Maragha Observatory's 750th year
anniversary, Maragha, Iran} \hfill(2009)
\begin{itemize} 
\item Rahmani, S., Mashhoon, M., Moghaddam , A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
\end{itemize}
\subsubsection*{Conferences Posters}
{\sl Statistical challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
\begin{itemize} 
\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
\end{itemize}

{\sl From galactic to extra galactic star formation (GESF), Marsseile, France}\hfill (2014)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Which Star formation laws in M31?" 
\end{itemize}

{\sl Canadian Astronomical Society Conference (CASCA), University of British Colombia, BC}\hfill (2013)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Effects of Gas Clouds and Existing Stars on Current Star Formation in M31: Testing the Extended Schmidt Law" 
\end{itemize}

\end{document}

### 2016-07-18 version0.0/paper1.tex
Added CV

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha\ luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/star.eps}
\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $\mathrm{F}_{3.6 \mu \mathrm{m}}$ and $\mathrm{F}_{4.5 \mu \mathrm{m}}$, though this was not mentioned in the aforementioned paper. 
Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

>>>>

\subsection{Stellar Initial Mass Function}
\label{sec: imf_sfl}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha\ luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/star.eps}
\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ: eskew_sfl}.}
\label{fig:stellarmass}
\end{figure}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ: eskew_sfl}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf_sfl}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ: eskew_sfl} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $\mathrm{F}_{3.6 \mu \mathrm{m}}$ and $\mathrm{F}_{4.5 \mu \mathrm{m}}$, though this was not mentioned in the aforementioned paper. 
Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.
